Sufficient Conditions for Reachability in Automata Networks with Priorities

### 2015-02-03 parts/def-ph.tex
add def of support

Finally, a context (\pref{def:context}) extends the notion of state to a set of possible initial states:
\modMF{
to each automaton in the model, a context maps a set of local states in this automaton.
}
\begin{definition}[Context ($\Ctx$)]
\label{def:context}
  A \emph{context} $\ctx$ associates to each automaton in $\PHs$ a non-empty subset of its local states:
  $\forall a \in \PHs, \PHget{\ctx}{a} \subseteq \PHl_a \wedge \PHget{\ctx}{a} \neq \emptyset$.
  $\Ctx$ is the set of all contexts.
\end{definition}
\noindent
For a given context $\ctx$, we note $a_i \in \ctx$ if and only if $a_i \in \PHget{\ctx}{a}$,
and for all $ps \in \powerset(\PHproc)$ or $ps \in \PHl$, $ps \subseteq \ctx \EQDEF \forall a_i \in ps, a_i \in \ctx$.
\begin{comment}
A sequence of actions $\delta$ is \emph{playable} in a context $\ctx$ if and only if 
$\exists s \subseteq \ctx, \delta \in \Sce(s)$.
We denote then: $\delta \in \Sce(\ctx)$,
and the play of $\delta$ in $\ctx$ is $\ctx \PHplay \delta = \ctx \Cap \ceil(\delta)$,
where $\ceil(\delta)$ is the set containing the last local state in the sequence $\delta$ (hitter or bounce) of every automaton mentioned in $\delta$.

@@

>>>>

A context (\pref{def:context}) extends the notion of state to a set of possible initial states:
\modMF{
to each automaton in the model, a context maps a set of local states in this automaton.
}
\begin{definition}[Context ($\Ctx$)]
\label{def:context}
  A \emph{context} $\ctx$ associates to each automaton in $\PHs$ a non-empty subset of its local states:
  $\forall a \in \PHs, \PHget{\ctx}{a} \subseteq \PHl_a \wedge \PHget{\ctx}{a} \neq \emptyset$.
  $\Ctx$ is the set of all contexts.
\end{definition}
\noindent
For a given context $\ctx$, we note $a_i \in \ctx$ if and only if $a_i \in \PHget{\ctx}{a}$,
and for all $ps \in \powerset(\PHproc)$ or $ps \in \PHl$, $ps \subseteq \ctx \EQDEF \forall a_i \in ps, a_i \in \ctx$.
\begin{comment}
A sequence of actions $\delta$ is \emph{playable} in a context $\ctx$ if and only if 
$\exists s \subseteq \ctx, \delta \in \Sce(s)$.
We denote then: $\delta \in \Sce(\ctx)$,
and the play of $\delta$ in $\ctx$ is $\ctx \PHplay \delta = \ctx \Cap \ceil(\delta)$,
where $\ceil(\delta)$ is the set containing the last local state in the sequence $\delta$ (hitter or bounce) of every automaton mentioned in $\delta$.

@@

Finally, we define the support (\pref{def:supp}) of a sequence of actions $\zeta$
as the set containing the first local state of each automata appearing in $\zeta$,
that is, as a hitter or as a target.
For this, we first define the \emph{first appearance} of an automata
in this sequence.

\begin{definition}[$\supp$ \& $\first$]
\label{def:supp}
  For all sequences of actions $\zeta$, we define:
  \[
    \suppf{\zeta} = \bigcup_{a \in \PHs} \firstf{a}{\zeta}
  \]
  where:
  \begin{align*}
  \forall a \in \PHs, \firstf{a}{\zeta} &=
    \begin{cases}
      \emptyset &
        \text{if } \forall n \in \indexes{\zeta},
        B^\zeta_n \cap \PHl_a \neq \emptyset \\
      B^\zeta_m \cap \PHl_a &
        \text{else, if } m =
        \min\{ n \in \indexes{\zeta} \mid B^\zeta_n \cap \PHl_a \neq \emptyset \}
    \end{cases} \\
  \forall n \in \indexes{\zeta}, B^\zeta_n &= \hitter{\zeta_n} \cup \{ \target{\zeta_n} \}.
  \end{align*}
\end{definition}

We note that for all sequence of actions $\zeta$,
$\forall a \in \PHs, 0 \leq \card{\firstf{a}{\zeta}} \leq 1$,
because given the particular for of the actions of an AAN (see \pref{def:ph}),
$\forall n \in \indexes{\zeta}, B_n \in \PHsublset[\PHl]$.
This also means that: $\suppf{\zeta} \in \PHsublset[\PHl]$.
